---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: embed
---

<style>                     
.navbar, [data-toggle=tab], .navbar-brand  {   background-color:darkgreen!important;   border-color:black;   color:whtie!important;
}


</style>  


# Project Budget Hours
```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(readxl)
library(kableExtra)
library(plotly)
library(DT)
library(lubridate)
```

```{r include=FALSE}
ProjectA <- read_excel("Hours_Predict_R.xlsx",
                       sheet = "Project A",
                       range = "B2:G100",
                       col_names = TRUE)

ProjectB <- read_excel("Hours_Predict_R.xlsx",
                       sheet = "Project B",
                       range = "B2:G100",
                       col_names = TRUE)

ProjectC <- read_excel("Hours_Predict_R.xlsx",
                       sheet = "Project C",
                       range = "B2:G100",
                       col_names = TRUE)


summary(ProjectA)
summary(ProjectB)
summary(ProjectC)

### to get this we will need to mutate
ProjectA <- ProjectA %>% 
  mutate(ProjectA = "ProjectA")
ProjectB <- ProjectB %>% 
  mutate(ProjectA = "ProjectB")
ProjectC <- ProjectC %>% 
  mutate(ProjectA = "ProjectC")

Project_data <- bind_rows(ProjectA,ProjectB,ProjectC)

### Join the table into one

Project_data <- bind_rows(ProjectA,ProjectB,ProjectC) ##Becasue they have the same column names, we can bind the data frame rows.

Project_data <- Project_data %>%   ##Deletes rows with NA
  na.omit()

Project_data <- Project_data %>% 
  rename(Project_Name = ProjectA)

### New row using Calculation: Mutate
# Mutate(new_col_name = calculation you want)

Project_data <- Project_data %>%
  mutate(percent = round((Actuals/Budget)*100,2))

Project_data <-Project_data %>% 
  mutate(OverUnder = case_when(Budget > Actuals ~ "Under Budget",  ## Case_when can be thought of an as IF function
                               Budget == Actuals ~ "On Budget",
                               TRUE ~ "Over Budget"))


## Count the number of tasks over or under budget
over_under_counts <- Project_data %>% 
  count(OverUnder) %>% 
  rename(Count = n) %>% 
  rename('Budget Status' = OverUnder) ##rename column name rename(new_name = previous_name)
```


Column {data-width=640}
-----------------------------------------------------------------------

### Project hours

```{r}

windowsFonts(`Century Gothic` = windowsFont("Century Gothic"))
g <- ggplot(Project_data, aes(x = Task, y = Actuals, fill = OverUnder, text = paste(percent, "%")))+
  geom_col()+
  facet_wrap(vars(Project_Name), scales = "free", shrink = FALSE, ncol = 3)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Century Gothic"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(family = "Century Gothic", size = 15),
        panel.background = element_rect(fill = "white"),
        strip.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = 0.5, family = "Century Gothic", size = 18),
        legend.title = element_text(family = "Century Gothic"))+
  scale_fill_manual(values = c("red","darkgreen"))+
  labs(title = "Project Hours",
       fill = "Budget Status")+
  ylab("Actuals (hrs)")
ggplotly(g)
```

Column {data-width=400}
-----------------------------------------------------------------------

### Total Task Budget Status

```{r}
# over_under_counts %>% kbl() %>% 
#   kable_styling(bootstrap_options = c("hover"))

valueBox(value = over_under_counts$Count[1], icon = "fa-bell", color = "#ffcccb",caption = "Number of Tasks Over Budget")

```

### Tasks Under Budget

```{r}
valueBox(value = over_under_counts$Count[2], icon = "fa-check", color = "#2ff900")

```

```{r include=FALSE}
calendar_data_excel <- read_excel("flexDashBoard_ghentdata.xlsx",
                                  sheet = "Sheet1",
                                  range = "B1:V50")

calendar_data_excel <- calendar_data_excel %>% 
  pivot_longer(cols = c(2:12),
               values_to = "status",
               names_to = "month")
calendar_data_excel <- calendar_data_excel %>%
  pivot_longer(cols = c(2:10),
               values_to = "name",
               names_to = "member")
calendar_data_excel <- calendar_data_excel %>% drop_na()

start_end_dates <- read_excel("flexDashBoard_ghentdata.xlsx",
                              sheet = "Sheet2",
                              range = "B2:D5")
join_the_tables <- inner_join(calendar_data_excel, start_end_dates, by= "Projects")

join_the_tables$Start <- ymd(join_the_tables$Start)
join_the_tables$End <- ymd(join_the_tables$End)

new_table <- join_the_tables %>% 
  pivot_longer(cols = c(6:7),
               names_to = "start/end",
               values_to = "dates")

```

### Staff Project Schedules
```{r}
ggplot(new_table, aes(x= dates, y= name, color= Projects))+
  geom_line(alpha = 0.5, size =5)+
  geom_vline(xintercept = today(), color = "black", size = .5, alpha= 0.7)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Century Gothic"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(family = "Century Gothic", size = 15),
        axis.text.y = element_text(family = "Century Gothic", size = 10),
        panel.background = element_rect(fill = "white"),
        strip.background = element_rect(fill = "white"),
        legend.background = element_rect(color = "white"),
        legend.title.align = 0.5,
        legend.text = element_text(family = "Century Gothic"),
        legend.key = element_rect(fill = "white"),
        plot.title = element_text(hjust = 0.5, family = "Century Gothic", size = 18),
        legend.title = element_text(family = "Century Gothic"))+
  xlab("Dates")+
  ylab("Names")+
  ggtitle("Staff Project Timelines")

```

# Budget Used



Column {data-width=640}
-----------------------------------------------------------------------
### Hours Spent on Projects by Employee
```{r}
ggplot(data = Project_data, aes(x= reorder(`Team Member`,-Actuals),y= Actuals))+geom_col(fill = "darkgreen")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, family = "Century Gothic"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(family = "Century Gothic", size = 15),
        panel.background = element_rect(fill = "white"),
        strip.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = 0.5, family = "Century Gothic", size = 18),
        legend.title = element_text(family = "Century Gothic"))+
  ylab("Proejct Hours")+
  ggtitle("Time Spent on Projects")

```



Column {data-width=400}
-----------------------------------------------------------------------

```{r include=FALSE}
budget_spend<- data.frame(buget_percent = c(85.3,56.8,18.65))


gauge(budget_spend$buget_percent[1], min = 0, max = 100, symbol = "%", gaugeSectors(
  success = c(0,20),warning = c(21,70),danger = c(71,100)
))
```

### ProjectA % of Budget Used
```{r}


gauge(budget_spend$buget_percent[1], min = 0, max = 100, symbol = "%", gaugeSectors(
  success = c(0,20),warning = c(21,70),danger = c(71,100)
))
```


### ProjectB % of Budget Used
```{r}
 gauge(budget_spend$buget_percent[2], min = 0, max = 100, symbol = "%", gaugeSectors(
  success = c(0,20),warning = c(21,70),danger = c(71,100)
))
```



### ProjectC % of Budget Used
```{r}

gauge(budget_spend$buget_percent[3], min = 0, max = 100, symbol = "%", gaugeSectors(
  success = c(0,20),warning = c(21,70),danger = c(71,100)
))

```

<!-- ### Plot -->
<!-- ```{r} -->
<!-- ggplot(data = Project_data, aes(Role, Actuals))+geom_point() -->
<!-- ``` -->



Column {data-width=200}
-----------------------------------------------------------------------

### Average CBA Hours
```{r include=FALSE}
#icons
# https://ionic.io/ionicons/v2/cheatsheet.html

projects_CBA <- Project_data %>% 
  filter(Category == "CBA")

CBA_mean_time_to_complete <- round(mean(projects_CBA$Actuals))

projects_facillites <- Project_data %>% 
  filter(Category == "Facilites")
	
Facilites_mean_time_to_complete <- round(mean(projects_facillites$Actuals))

Transportation_mean_time <- Project_data %>% 
  filter(Category == "Transportation")

Trasnsportation_mean_time_to_complete <- round(mean(Transportation_mean_time$Actuals))

projects_staffing <- Project_data %>% 
  filter(Category == "Staffing")

staffing_mean_complete_time <- round(mean(projects_staffing$Actuals))


```


```{r}
valueBox(CBA_mean_time_to_complete, color = "#8a2be2", icon = "fa-pen")


```



### Average Facilities Hours
```{r}
valueBox(Facilites_mean_time_to_complete, color = "green", icon = "fa-school", caption = " Average Facilities Hours")

```


### Transportation
```{r}
valueBox(Trasnsportation_mean_time_to_complete, color = "yellow", icon = "fa-bus", caption = " Average Transportation Hours")

```

### Staffing
```{r}
valueBox(staffing_mean_complete_time, color = "lightblue", icon = "ion-android-people", caption = "Average Staffing Hours")
```


